---
title: "Introduction to fastscoRe"
author: "Chris Comiskey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

Three [pillars](https://opendatagroup.github.io/Reference/FastScore%20API/). 

- Connect
- Model Manage
- Engine

All inherit from initial FastScore API instance. 

## Instance Class

Create FastScore API client with `Instance` class generator.

```{r, eval = FALSE}
api_cli <- fastscoRe::Instance$new(basePath = "https://localhost:8000")
```

## Connect Class

FastScore doc [page](https://opendatagroup.github.io/Reference/FastScore%20API/Connect/)

## Model Manage Class

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Engine Class

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

